\section{Abstract} 
This is a small case study in the 2012 release of the Ada programming language. The motivation of this case study is to expose one to the broadest topics of the Ada programming language via a detailed example. The topic I have chosen is to write up a very simple web server. A web server typically, has to deal with the following aspects:
\begin{itemize}
\item Concurrency
\item Sockets, and messaging
\item The Protocol (in this case \textbf{http})
\item Different Filesystems support
\end{itemize} 
This document is hoped to help the curious reader to learn the aspects of the language with a little more ease, introduce the http protocol slightly, and provide references where possible to direct to sources for more exploration. I also record personal notes. 
There is a core aim, to present the aforementioned array of topics to the reader, in a project that is not too big, and intimidate the beginner, and not too small to not be of any learning use. We try and achieve this balance by reducing the lines of code and sacrificing aspects of software architecture\footnote{In the code base, you might notice some aspects that could be factored out, or areas where coupling could be reduced. This will be done on purpose in order to reduce the amount of indirection, and ease the quick navigation, reading and understanding for the reader.} in order achieve this.

\subsection{Disclaimer}
As previously stated, this is a case study that is worked on by a complete beginner in the Ada2012 programming language. You might find that this paper is referencing a lot of sources, in a collage fashion. That may be a true fact, but the purpose of this paper is not to shed new light to a problem. This paper is aimed as a tutorial and reference notes to the programming language, for the beginners and intermediate programmers. Please also consider using the excellent references, as they have provided a lot of help in this case study, and can be used more to broaden ones' knowledge.

\subsection{The name `Axios'}
Axios stands for ``Ada eXtra ineffectual Object Oriented Server''. And it is just that!
